---
title: "Testing Plot Accessibility"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
---

```{r xaringanthemer, include=FALSE}
library(xaringanthemer)
library(ggplot2)
style_duo_accent(colors = c(yellow = "#f3b61f"))
```

```{r lemur-pop-setup, include=FALSE}
set.seed(4242)
lemurs <- tibble::tibble(
  year = 2000:2020,
  population = 500 + (25 * (year - 2000)) + floor(runif(length(year), -50, 50))
)
```

These slides test various approaches to increasing the accessibility of plots in xaringan slides.
The code for the plot is presented in a later slide.

The test on the next slide uses the slide heading as the plot title. The code is hidden and the `fig.alt` chunk option is used to add alt text to the plot. The data in the plot is printed in a visually hidden block after the image.

---

# Lemur Population

```{r lemur-pop, fig.width=10, fig.height=4.5, echo=FALSE, out.width="100%", dev="svg", fig.alt = "Line chart of a simulated lemur population from 2000 to 2020."}
ggplot(lemurs) +
  aes(year, population) +
  geom_line(size = 2) +
  labs(x = NULL, y = NULL, title = NULL) +
  theme_xaringan()
```

.visually-hidden[
The line chart contains the following data:

```{r echo=FALSE}
knitr::kable(lemurs, format.args = list(big.mark = ","))
```
]

<style>
/* https://github.com/h5bp/main.css/issues/12#issuecomment-451965809 */
.visually-hidden {
  position: absolute;
  width: 1px;
  height: 1px;
  margin: 0;
  padding: 0;
  overflow: hidden;
  clip: rect(0 0 0 0);
  -webkit-clip-path: inset(50%);
          clip-path: inset(50%);
  border: 0;
  white-space: nowrap;
}
</style>

---

The test on the next slide uses the plot as the slide's background image.
The visually hidden block is used again with a table containing the data.

---
background-image: url(`r knitr::fig_chunk("lemur-pop-plot", "svg")`)
background-size: 90%

.visually-hidden[
This slide shows a line chart of a simulated lemur population from 2000 to 2020.

```{r echo=FALSE}
knitr::kable(lemurs, format.args = list(big.mark = ","))
```
]

---

I tested directly embedding the SVG file here, but it very much did not work.

---

# Code for the plot

```{r ref.label="lemur-pop-setup"}
```

```{r lemur-pop-plot, fig.width=16 * 2/3, fig.height=9 * 2/3, dev="svg", fig.show="hide"}
library(ggplot2)
ggplot(lemurs) +
  aes(year, population) +
  geom_line(size = 2) +
  labs(x = NULL, y = NULL, title = "Lemur Population") +
  theme_xaringan()
```
